---
title: "Introduction to saproj"
author: "Dan Kary"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to saproj}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The `saproj` package has two basic purposes:

1. Presenting guidelines for organizing R-based analyses.
2. Providing a way to automate the creation of project folders/files within these guidelines.

## R Prerequisites

Familiarity with a few topics is required to use `saproj` effectively:

- [R Basics](https://www.rstudio.com/online-learning/#R). The [Base R Cheatsheet](https://www.rstudio.com/wp-content/uploads/2016/10/r-cheat-sheet-3.pdf) provides a very nice reference.
- Familiarity with the [tidyverse](https://blog.rstudio.org/2016/09/15/tidyverse-1-0-0/) generally and [dplyr](https://cran.rstudio.com/web/packages/dplyr/vignettes/introduction.html) in particular

### Recommended

- [RMarkdown](http://rmarkdown.rstudio.com/lesson-1.html) for a notebook interface and convenient analysis documentation
- [R for Data Science](http://r4ds.had.co.nz/) for further reading

## Starting a Project

To begin analysis on a Project:

1. Create a new project in RStudio by clicking *File > New Project* (see [RStudio Projects](http://r4ds.had.co.nz/workflow-projects.html) for an introduction).

2. Run `saproj::new_project` from the Console. This will create a set of folders & files like those shown below.

Dan note - Insert a screenshot of the new project structure here

A template directory structure is useful...

code/
data/
out/
    template.Rmd
README

### Directory Structure 

## Example Projects

### A minimal example 

- See about providing some sample data (probably just use the data in the tablr package). 
- It would also be useful to load data using haven (I probably will want to deprecate tablr usage)
- Also make modifications to lichist (salic) with some simplifications
    + not using print functions
    + (maybe) removing some functions for checking etc. (i might just clean that up later)

(load, clean, do)

### A more complex example 

(1-prep, 2-profiles, 3-results)



## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, results='asis'}
knitr::kable(head(mtcars, 10), caption = "test caption")
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
